Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-14 analysis/paper/sim_survey_paper.Rmd
Exploring alternate figures for paper

```{r sp-fig, cache = TRUE, fig.height = 3.8, fig.width = 8.5, fig.cap = "- An example from year seven of the simulation of a) the distribution of total abundance available to the survey, and b) locations of the sets conducted and total numbers caught in a stratified random survey with a set density of 0.002 sets / km^2^."}

@@

```{r est-fit, cache = TRUE, fig.height = 9, fig.width = 8.5, fig.cap = "- Stratified estimates of abundance at age across years from 10 simulations of a survey with a set density of 0.002 sets / km^2^ and sampling caps of 500 lengths per set and 10 ages per length group. The heavy dark line indicates the true tred in the population available to the survey."}

@@

d <- sim$age_strat_error
d <- d[d$survey == which_survey & d$sim %in% 1:10, ]
d$age[d$age > 15] <- 15 # aggregate beyond 15
d$age <- as.character(d$age)
d$age[d$age == "15"] <- "15+"
d$age <- factor(d$age, levels = c(as.character(1:14), "15+"))
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), by = c("year", "age", "sim")]

p <- ggplot(data = d) + 
  geom_line(aes(x = year, y = I_hat, color = sim, group = sim), size = 0.3) +
  geom_line(aes(x = year, y = I), color = viridis::viridis(1), size = 0.7) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_wrap(~age, scales = "free_y", dir = "v", nrow = 5) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

cowplot::save_plot(plot = p, filename = "analysis/paper/figures/true_vs_est.pdf",
                   base_height = 9, base_width = 8.5)
p

@@

>>>>

```{r sp-fig, cache = TRUE, fig.height = 3.8, fig.width = 8.5, fig.cap = "- An example from year seven of the simulation of a) the distribution of total abundance available to the survey, and b) locations of the sets conducted and total numbers caught in a stratified random survey with a set density of 0.002 sets / km^2^. Grey lines indicate depth-based survey strata."}

@@

```{r est-fit, cache = TRUE, fig.height = 8, fig.width = 7, fig.cap = "- Stratified estimates of abundance at age across years from 10 simulations of a survey with a set density of 0.002 sets / km^2^ and sampling caps of 500 lengths per set and 10 ages per length group. The heavy dark line indicates the true tred in the population available to the survey."}

@@

d <- sim$age_strat_error
d <- d[d$survey == which_survey & d$sim %in% 1:1000, ]
d$age[d$age > 8] <- 8 # aggregate beyond 10
d$age <- as.character(d$age)
d$age[d$age == "8"] <- "8+"
d$age <- factor(d$age, levels = c(as.character(1:7), "8+"))
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), by = c("year", "age", "sim")]

p <- ggplot(data = d) + 
  geom_line(aes(x = year, y = I_hat, color = sim, group = sim), size = 0.1) +
  geom_line(aes(x = year, y = I), color = viridis::viridis(1), size = 0.7) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_wrap(~age, scales = "free_y", dir = "v", nrow = 4) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

cowplot::save_plot(plot = p, filename = "analysis/paper/figures/true_vs_est.pdf",
                   base_height = 8, base_width = 7)
p

@@

```{r age-fig, fig.width = 7, fig.height = 6}

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_year <- 5

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$sim %in% 1:1000 & d$year == which_year & d$set_den %in% which_set_dens &
         d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]
d$age[d$age > 8] <- 8 # aggregate beyond 8
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), 
       by = c("year", "age", "sim", "survey", "set_den", "lengths_cap")]

p <- ggplot(data = d) + 
  geom_line(aes(x = age, y = I_hat, color = sim, group = sim), size = 0.1) +
  geom_line(aes(x = age, y = I), color = viridis::viridis(1), size = 0.5) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_grid(set_den ~ lengths_cap) +
  xlab("Age") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0), 
                     labels = c("2", "4", "6", "8+"), 
                     breaks = seq(2, 8 , 2)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

```{r year-fig, fig.width = 7, fig.height = 6}

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_age <- 4

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$sim %in% 1:1000 & d$age == which_age & d$set_den %in% which_set_dens &
         d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]

p <- ggplot(data = d) + 
  geom_line(aes(x = year, y = I_hat, color = sim, group = sim), size = 0.1) +
  geom_line(aes(x = year, y = I), color = viridis::viridis(1), size = 0.5) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_grid(set_den ~ lengths_cap) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))
